Think deep for reef resilience

### 2025-08-04 paper/paper_draft.qmd
Slight expansion of the connectivity section

Twenty-four total days of connectivity data were used in this investigation, 2015, 2016,
2018 and 2019 are represented represented by 3 daily connectivity matrices each, while 2017
and 2020 are represented with 5 daily matrices each. Connectivity levels are implemented in
ADRIA - CoralBlox as mean over the 24 days for each location.

>>>>

Connectivity data from 24 days in total were used in this investigation. These data span six
years: 2015, 2016, 2018, and 2019 are each represented by 3 daily connectivity matrices, while
2017 and 2020 are each represented by 5 daily matrices. Indicative connectivity strengths are
implemented in ADRIA-CoralBlox as the mean of all available data for each location (i.e.,
all 24 days). While the connectivity strengths do not vary from year to year within the
simulation, they do vary between reefs of varying sizes, providing sufficient heterogeneity
to capture spatial patterns in larval dispersal and settlement dynamics. The spatial
variability also enables investigations into the influence of connectivity strength and its
role in driving recovery processes.
